---
title: "Challenge-7"
author: "Ho Zhi Yi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# All about ggplot2 package

Data: Palmer Penguins
```{r, eval=TRUE}
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)
```

Palmer Penguins: Plot recreation
```{r, eval=TRUE}
ggplot(data = penguins,
 mapping = aes(x = bill_depth_mm,
               y = bill_length_mm,
               colour = species)) +
  geom_point() +
  labs(title = "Bill depth and length",
       subtitle = "Dimensions for Adelie, Chinstrap, and Gentoo Penguins",
       x = "Bill depth (mm)", y = "Bill length (mm)",
       colour = "Species",
       caption = "Source: Palmer Station LTER",
   scale_colour_viridis_d())
```

Palmer Penguins: Argument names
```{r, eval=TRUE}
ggplot(penguins,
 aes(x = bill_depth_mm,
 y = bill_length_mm,
 colour = species)) +
 geom_point() +
 scale_colour_viridis_d()


ggplot(penguins) + # Data layer
 aes(x = bill_depth_mm,
 y = bill_length_mm,
 colour = species) + # Aesthetics layer
 geom_point() + # Geometric layer
 scale_colour_viridis_d()
```

Palmer Penguins: Colour
```{r, eval=TRUE}
ggplot(penguins) + aes(x = bill_depth_mm, y = bill_length_mm,
 colour = species) +
 geom_point() + scale_colour_viridis_d()
```

Palmer Penguins: Shape
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
 shape = island)) +
 geom_point() + scale_colour_viridis_d()


ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
 shape = species)) +
 geom_point() + scale_colour_viridis_d()
```

Palmer Penguins: Size
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species, shape = species,
 size = body_mass_g)) +
 geom_point() + scale_colour_viridis_d()
```

Palmer Penguins: Alpha
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, colour = species,
 shape = species, size = body_mass_g, alpha = flipper_length_mm)) +
 geom_point() + scale_colour_viridis_d()
```

Mapping vs. Setting
```{r, eval=TRUE}
#Mapping 
ggplot(penguins) +
 aes(x = bill_depth_mm,
 y = bill_length_mm,
 size = body_mass_g,
 alpha = flipper_length_mm) +
 geom_point()

#Setting
ggplot(penguins) +
 aes(x = bill_depth_mm,
 y = bill_length_mm) +
 geom_point(size = 2, alpha = 0.5)
```

Faceting
```{r, eval=TRUE}
ggplot(penguins) +
 aes(x = bill_depth_mm,
 y = bill_length_mm) +
 geom_point() +
 facet_grid(species ~ island)
```

Facet 2
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_grid(species ~ sex)
```

Facet 3
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_grid(sex ~ species)
```

Facet 4
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_wrap(~ species)
```

Facet 5
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_wrap(~ species, ncol = 2)
```

Facet 6
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
 facet_grid(. ~ species)
```

Facet and Colour
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
 geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d()
```

Face and color, no legend
```{r, eval=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm, color = species)) +
 geom_point() + facet_grid(species ~ sex) + scale_color_viridis_d() +
 guides(color = "none")
```

# Visualizing numeric variables
```{r, eval=TRUE}
#peek data
library(openintro)
glimpse(loans_full_schema)
```

Selected variables
```{r, eval=TRUE}
loans <- loans_full_schema %>%
 select(loan_amount, interest_rate, term, grade,
 state, annual_income, homeownership, debt_to_income)
glimpse(loans)
```

Histogram
```{r, eval=TRUE}
ggplot(loans) + aes(x = loan_amount) +
 geom_histogram()
```

Histograms and binwidth=1000
```{r, eval=TRUE}
# binwidth = 1000
ggplot(loans, aes(x = loan_amount)) +
 geom_histogram(binwidth = 1000)
```

Histograms and binwidth = 5000
```{r, eval=TRUE}
# binwidth = 5000
ggplot(loans, aes(x = loan_amount)) +
 geom_histogram(binwidth = 5000)
```

Histograms and binwidth=20000
```{r, eval=TRUE}
# binwidth = 20000
ggplot(loans, aes(x = loan_amount)) +
 geom_histogram(binwidth = 20000)
```

Customizing histograms
```{r, eval=TRUE}
ggplot(loans, aes(x = loan_amount)) + geom_histogram(binwidth = 5000) +
 labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club loans" )
```

Fill with a categorical variable
```{r, eval=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
 geom_histogram(binwidth = 5000, alpha = 0.5) +
 labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans")
```

Facet with a categorical variable
```{r, eval=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) + geom_histogram(binwidth = 5000) +
 labs(x = "Loan amount ($)",y = "Frequency",title = "Amounts of Lending Club loans") +
 facet_wrap(~ homeownership, nrow = 3)
```

Density plot
```{r, eval=TRUE}
ggplot(loans, aes(x = loan_amount)) +
 geom_density()
```

Density plots and adjusting bandwidth
```{r, eval=TRUE}
ggplot(loans, aes(x = loan_amount)) +
 geom_density(adjust = 0.5)

ggplot(loans, aes(x = loan_amount)) +
 geom_density(adjust = 1) # default bandwidth

ggplot(loans, aes(x = loan_amount)) +
 geom_density(adjust = 2)
```

Customizing density plots
```{r, eval=TRUE}
ggplot(loans, aes(x = loan_amount)) +
 geom_density(adjust = 2) +
 labs( x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans" )
```

Adding a categorical variable
```{r, eval=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
 geom_density(adjust = 2, alpha = 0.5) +
 labs(x = "Loan amount ($)",y = "Density",title = "Amounts of Lending Club loans", fill = "Homeownership")
```

Box plot
```{r, eval=TRUE}
ggplot(loans, aes(x = interest_rate)) +
 geom_boxplot()
```

Box plot and outliers
```{r, eval=TRUE}
ggplot(loans, aes(x = annual_income)) +
 geom_boxplot()
```

Customizing box plots
```{r, eval=TRUE}
ggplot(loans, aes(x = interest_rate)) +geom_boxplot() +labs(x = "Interest rate (%)",y = NULL,
 title = "Interest rates of Lending Club loans") +
 theme( axis.ticks.y = element_blank(), axis.text.y = element_blank() )
```

Adding a categoric variable
```{r, eval=TRUE}
ggplot(loans, aes(x = interest_rate,
 y = grade)) +
 geom_boxplot() +
 labs(x = "Interest rate (%)",y = "Grade",title = "Interest rates of Lending Club loans",subtitle = "by grade of loan")
```

Scatterplot
```{r, eval=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
 geom_point()
```

Hex plot
```{r, eval=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
 geom_hex()


ggplot(loans %>% filter(debt_to_income < 100),
 aes(x = debt_to_income, y = interest_rate)) +
 geom_hex()
```

# Visualizing categoric variables

Bar plot
```{r, eval=TRUE}
ggplot(loans, aes(x = homeownership)) +
 geom_bar()
```

Segmented bar plot
```{r, eval=TRUE}
ggplot(loans, aes(x = homeownership,
 fill = grade)) +
 geom_bar()


ggplot(loans, aes(x = homeownership, fill = grade)) +
 geom_bar(position = "fill")
```

Customizing bar plots
```{r, eval=TRUE}
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
labs( x = "Proportion", y = "Homeownership", fill = "Grade", title = "Grades of Lending Club loans")
```

#  Visualizing variables of varied types

Violin plots
```{r, eval=TRUE}
ggplot(loans, aes(x = homeownership, y = loan_amount)) +
 geom_violin()
```

Ridge plots
```{r, eval=TRUE}
library(ggridges)
ggplot(loans, aes(x = loan_amount, y = grade, fill = grade, color = grade)) +
 geom_density_ridges(alpha = 0.5)
```

