---
title: "Challenge-6"
author: "Ho Zhi Yi"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Countdown Blastoff (While Loop)

Create a program that simulates a rocket launch countdown using a while loop. Start from 10 and countdown to "Blastoff!" with a one-second delay between each countdown number. Print a message when the rocket launches.

**Hint:** You may want to use `cat` command to print the countdown and `Sys.sleep` for incorporating the delay

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
i <- 10
while (i <= 10 && i > 0) {
  cat(i,"...")
  Sys.sleep(1)
  i <- i-1
}
print("Blastoff!")

```
<br>

#### Question-2: Word Reverser (for Loop)

Develop a program that takes a user-entered word and uses a while loop to print the word's characters in reverse order. For example, if the user enters "hello," the program should print "olleh."

**Hint:** You may want to use `substr` command to access each character of the input word, and `paste` command to join the reversed letters one at a time

**Solutions:** 

```{r, eval=FALSE,echo=TRUE}
# Enter code here

input <- readline("Enter a word: ")
reverse <- function() {
  i <- nchar(input)
  reversed <- ""
  while (i >= 1) {
    letter <- substr(input, i, i)
    reversed <- paste(reversed, letter, sep = "")
    i <- i - 1
  }
  return(reversed)
}

reverse()

```
<br>
