---
title: "Week-9 Final Project Documentation"
author: "Ho Zhi Yi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Webpage link

<https://zhizyii.github.io/>

## Project Documentations

1.  What is the topic that you have finalized? (Answer in 1 or 2 sentences)

-   **Topic:** Greenhouse Gas Emissions Trends in the World

-   Analyzing Greenhouse Gas Emissions Trends based on:

    -   industry

    ```{r, eval=TRUE, warning=FALSE}
    library(dplyr)
    # read csv file
    data <- read.csv("Annual_Greenhouse_Gas_(GHG)_Air_Emissions_Accounts.csv")
    distinct(data,Industry)
    ```

    -   region

    ```{r, eval=TRUE}
    distinct(data,Country)
    ```

    -   gas types

    ```{r, eval=TRUE}
    distinct(data,Gas_Type)
    ```

2.  What are the data sources that you have curated so far? (Answer 1 or 2 sentences)

-   Annual greenhouse gas emissions by activity and by region (2010 to 2021)
