---
title: "Challenge-5"
author: "Ho Zhi Yi"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
<br>

#### Question-1: Local Variable Shadowing 

Create an R function that defines a global variable called `x` with a value of 5. Inside the function, declare a local variable also named `x` with a value of 10. Print the value of `x` both inside and outside the function to demonstrate shadowing.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
x <- 5

func <- function(){
  x = 10
  return(x)
}

x
func()
```
<br>

#### Question-2: Modify Global Variable

Create an R function that takes an argument and adds it to a global variable called `total`. Call the function multiple times with different arguments to accumulate the values in `total`.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
total = 0

func <- function(arg){
  total <<- total + arg
}

func(10)
func(5)
total
```
<br>

#### Question-3: Global and Local Interaction 

Write an R program that includes a global variable `total` with an initial value of 100. Create a function that takes an argument, adds it to `total`, and returns the updated `total`. Demonstrate how this function interacts with the global variable.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
total = 100

func <- function(arg){
  total <<- total + arg
  return(total)
}

func(20)
```
<br>

#### Question-4: Nested Functions

Define a function `outer_function` that declares a local variable `x` with a value of 5. Inside `outer_function`, define another function `inner_function` that prints the value of `x`. Call both functions to show how the inner function accesses the variable from the outer function's scope.

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
outer_function <- function(){
  x <- 5
  inner_function <- function(){
    print(x)
  }
  inner_function()
}

outer_function()
```
<br>

#### Question-5: Meme Generator Function

Create a function that takes a text input and generates a humorous meme with the text overlaid on an image of your choice. You can use the `magick` package for image manipulation. You can find more details about the commands offered by the package, with some examples of annotating images here: https://cran.r-project.org/web/packages/magick/vignettes/intro.html

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
library(magick)
tiger <- image_read_svg('http://jeroen.github.io/images/tiger.svg', width = 350)

# Enter code here
meme <- function(text_input){
  image_annotate(tiger,text_input,size = 60, gravity = "southwest", color = "green")
}
meme("IM HUNGRY")
```
<br>

#### Question-6: Text Analysis Game  

Develop a text analysis game in which the user inputs a sentence, and the R function provides statistics like the number of words, characters, and average word length. Reward the user with a "communication skill level" based on their input.

**Solutions:**

```{r, eval=FALSE,echo=TRUE}
# Enter code here
game <- function(){
  read <- readline(prompt = "Please enter a sentence: ")
  words <- length(strsplit(read, "\\s+")[[1]])
  chars <- nchar(read)
  av <- chars/words
  
  cat(" words:",words,"\n","characters:",chars,"\n","average word length:",av,"\n")
  
  if (av > 8){
    cat("Your communication skill level: EXCELLENT! ")
  } else if (av < 4){
    cat("Your communication skill level: meh :( ")
  } else {
    cat("Your communication skill level: not bad :D")
  }
}
game()
```
<br>